---
title: "Scalability"
output: html_document
params:
  pq: ""
---

Wall time against cell count, from one `collect.py` parquet.

    ./collect.py ../split-stages-plan/out_run
    Rscript -e 'rmarkdown::render("pca-scalability.Rmd", params = list(pq = "metrics_d327c077.parquet"))'

With `pq` left empty it falls back to the only `metrics_*.parquet` in the
working directory, and refuses to guess when there is more than one -- picking
an arbitrary run silently is how you plot last week's numbers by accident.

```{r setup, message = FALSE}
library(ggplot2)
pq <- params$pq
if (!nzchar(pq)) {
  found <- Sys.glob("metrics_*.parquet")
  if (length(found) != 1L)
    stop(sprintf("pass params = list(pq = ...): %d metrics_*.parquet here", length(found)))
  pq <- found
}
d <- nanoparquet::read_parquet(pq)
# rung id -> cells: tenx-0020k -> 20000
d$cells <- as.integer(sub(".*?(\\d+)k.*", "\\1", d$DATA_method)) * 1000

# One series per *configuration*, not per module. A module that sweeps a
# parameter has several rows at the same x -- pc-rapids and pc-biocsingular each
# run two solvers -- and colouring by `method` alone joins them into one
# sawtooth line instead of two curves.
#
# DATA is the other way round: this benchmark gives every ladder rung its own
# module id, so `method` there is the dataset, not a method. All six are one
# loader, so label them by the repo.
#
# ponytail: `PCA_solver` is the only sweep in this benchmark. Add the column
# here if another stage grows one, or key off `param_hash` if it gets tedious.
d$series <- ifelse(d$stage == "DATA", basename(d$repo),
                   ifelse(is.na(d$PCA_solver), d$method,
                          paste(d$method, d$PCA_solver, sep = ":")))
sc <- list(scale_x_log10(), scale_y_log10(), labs(x = "cells", y = "wall time (s)"))
```

## Per stage

```{r stages, fig.width = 9, fig.height = 5}
ggplot(d, aes(cells, perf_s, colour = series)) +
  geom_point() + geom_line() + facet_wrap(~ stage) + sc
```

## Peak RSS per stage

```{r stages_rss, fig.width = 9, fig.height = 5}
ggplot(d, aes(cells, perf_max_rss, colour = series)) +
  geom_point() + geom_line() + facet_wrap(~ stage) + sc + labs(y = "peak RSS (MB)")
```

## PCA methods

```{r pca, fig.width = 7, fig.height = 4.5}
p <- subset(d, stage == "PCA")
ggplot(p, aes(cells, perf_s, colour = series)) +
  geom_point() + geom_line() + sc + labs(colour = "method")
```
